---
title: "Phoenix Housing Market Info"
---


This document contains some information I have been monitoring relating to real estate conditions in Phoenix, AZ.  




```{r MortageIndices,  out.width='100%', echo=FALSE}
library(tidyverse) #Core Data Analysis Tools
library(tidyquant) # Quantitative Analysis
library(plotly)  # Interactive Visualizations

g <- c( "OBMMIJUMBO30YF",# Jumbo 30 Yr Fixed
   "OBMMIFHA30YF",  # FHA_30yr
   "OBMMIC30YF",    #  Fixed_30yr Conforming
   "OBMMIC15YF"     # Fixed_15yr Conforming
   
   )  %>%
  
  tq_get(get  = "economic.data", from = "2022-01-01") %>% 
  rename(Name = symbol, Date = date, Percent = price) %>% 
  mutate(
    Percent == Percent %>% round(1),
    Name = case_when(
        Name == "OBMMIJUMBO30YF" ~ "Jumbo_30yr",
        Name == "OBMMIFHA30YF" ~   "FHA_30yr",
        Name == "OBMMIC30YF" ~     "Fixed_30yr",
        Name == "OBMMIC15YF" ~     "Fixed_15yr"),
    Name = as_factor(Name)) %>%
    
  na.omit %>%
  
  ## Data Visualization
  ggplot(aes(x=Date, y=Percent, color=Name)) +
  geom_line() +
  
  # Formatting
    labs(
        title = "Optimal Blue: Mortgage Rate Indices",
        x = "Date",
        y = "Percent",
        caption = "Optimal Blue, retrieved from FRED:\nFederal Reserve Bank of St. Louis\nhttps://fred.stlouisfed.org") +
    
    theme_tq() +
    theme(
        legend.position = "right",
        plot.title = element_text(face = "bold"),
        axis.title.x = element_blank(),
        plot.caption = element_text(face = "italic"),
        axis.text.x = element_text(angle=30, hjust=.5),
        plot.margin = margin(1,1,1.5,1.2, "cm")) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m-%y") +
  scale_y_continuous(breaks = seq(0,8,.5))
## plot 
plotly::ggplotly(g, tooltip = c("Date", "Percent")) %>% 
  layout(annotations = 
 list(x = 1, y = -0.1, 
      text = str_glue("Percent, Not Seasonally Adjusted, Source: Optimal Blue, retreived from  fred.stlouisfed.org"), 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='bottom', yanchor='bottom', xshift=0, yshift=-30,
      font=list(size=9, color="black")) 
 )
```

 - [30-Year Fixed Rate Jumbo Mortgage Index](https://fred.stlouisfed.org/series/OBMMIJUMBO30YF)
 - [30-Year Fixed Rate FHA Mortgage Index](https://fred.stlouisfed.org/series/OBMMIFHA30YF)
 - [30-Year Fixed Rate Conforming Mortgage Index](https://fred.stlouisfed.org/series/OBMMIC30YF)
 - [15-Year Fixed Rate Conforming Mortgage Index](https://fred.stlouisfed.org/series/OBMMIC15YF)

<br/>



```{r MortageRates,  out.width='100%', echo=FALSE}

library(tidyverse) #Core Data Analysis Tools
library(tidyquant) # Quantitative Analysis
library(plotly)  # Interactive Visualizations


g <- c( "MORTGAGE5US", # mortgageARM
   "MORTGAGE15US", # mortgage15
   "MORTGAGE30US",  # mortgage30
   "FEDFUNDS")  %>% # Federal Funds Rate
  
  ## 
  tq_get(get  = "economic.data", from = "2020-01-01") %>% 
  rename(Name = symbol, Date = date, Percentage = price) %>% 
  mutate(
    Name = case_when(
        Name == "MORTGAGE5US" ~ "ARM_5yr",
        Name == "MORTGAGE15US" ~ "Mortgage_15yr",
        Name == "MORTGAGE30US" ~ "Mortgage_30yr",
        Name == "FEDFUNDS" ~ "FedFundsRate"),
    Name = as_factor(Name)) %>%
  
  ## Data Visualization
  ggplot(aes(x=Date, y=Percentage, color=Name)) +
  geom_line() +
  
  # Formatting
    labs(
        title = "Freddie Mac: Average US Mortgage Rates",
        x = "Date",
        y = "Percentage",
        caption = "Freddie Mac, retrieved from FRED:\nFederal Reserve Bank of St. Louis\nhttps://fred.stlouisfed.org") +
    theme_tq() +
    theme(
        legend.position = "right",
        axis.title.x = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(face = "italic"),
        axis.text.x = element_text(angle=30, hjust=.5),
        plot.margin = margin(1,1,1.5,1.2, "cm")) + 
  scale_x_date(date_breaks = "3 month", date_labels = "%m-%y") + 
  scale_y_continuous(breaks = seq(0,8,.5))

## plot 
plotly::ggplotly(g, tooltip = c("Date", "Percentage")) %>%  
  layout(annotations = 
 list(x = 1, y = -0.1, 
      text = str_glue("Percent, Not Seasonally Adjusted, Source: Freddie Mac, retreived from fred.stlouisfed.org"), 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='bottom', yanchor='bottom', xshift=0, yshift=-35,
      font=list(size=9, color="black")) 
 )
```

Data Source:

 - [5 1-Year Adjustable Rate Mortgage Average](https://fred.stlouisfed.org/series/MORTGAGE5US)
 - [15-Year Fixed Rate Mortgage Average in the United States](https://fred.stlouisfed.org/series/MORTGAGE15US)
 - [30-Year Fixed Rate Mortgage Average in the United States](https://fred.stlouisfed.org/series/MORTGAGE30US)
 - [Federal Funds Effective Rate](https://fred.stlouisfed.org/series/FEDFUNDS)

<br/>



```{r MarketHotness, out.width='100%', echo=FALSE}

library(tidyverse) #Core Data Analysis Tools
library(tidyquant) # Quantitative Analysis
library(plotly)  # Interactive Visualizations


g <- c( "HOSCMSA38060", # Hotness Score
   "SUSCMSA38060", # Supply Score
   "DESCMSA38060" # Demand Score
   )  %>%
  
  ## 
  tq_get(get  = "economic.data", from = "2020-01-01") %>% 
  rename(Name = symbol, Date = date, Score = price) %>%
  group_by(Name) %>%
  mutate(
    PercentChange =((Score/lag(Score,2)-1)*100) %>% round(1),
    Name = case_when(
        Name == "HOSCMSA38060" ~ "Hotness Score",
        Name == "SUSCMSA38060" ~ "Supply Score",
        Name == "DESCMSA38060" ~ "Demand Score"
        ),
    Name = as_factor(Name))  %>%
  na.omit %>% ungroup(Name) %>% 
  
  ## Data Visualization
  ggplot(aes(x=Date, y=PercentChange, color=Name)) +
  geom_line() +
  
  # Formatting
    labs(
        title = "Market Hotness Scores",
        x = "Date",
        y = "MoM Percentage Change",
        caption = "Realtor.com, retrieved from FRED:\nFederal Reserve Bank of St. Louis\nhttps://fred.stlouisfed.org") +
    theme_tq() +
    theme(
        legend.position = "right",
        axis.title.x = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(face = "italic"),
        axis.text.x = element_text(angle=30, hjust=.5),
        plot.margin = margin(1,1,1.5,1.2, "cm")) + 
  scale_x_date(date_breaks = "3 month", date_labels = "%m-%y")#+ 
  #scale_y_continuous(breaks = seq(0,8,.5))

## plot 
plotly::ggplotly(g, tooltip = c("Date", "PercentChange")) %>%  
  layout(annotations = 
 list(x = 1, y = -0.1, 
      text = str_glue("Score, Not Seasonally Adjusted, Source: Realtor.com, retreived from fred.stlouisfed.org"), 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='bottom', yanchor='bottom', xshift=0, yshift=-35,
      font=list(size=9, color="black")) 
 )
```

 - [Market Hotness: Hotness Score in Phoenix-Mesa-Scottsdale, AZ](https://fred.stlouisfed.org/series/HOSCMSA38060)
 - [Market Hotness: Supply Score in Phoenix-Mesa-Scottsdale, AZ](https://fred.stlouisfed.org/series/SUSCMSA38060)
 - [Market Hotness: Demand Score in Phoenix-Mesa-Scottsdale, AZ](https://fred.stlouisfed.org/series/DESCMSA38060)
<br/>



```{r HousePrices, out.width='100%', echo=FALSE}

library(tidyverse) #Core Data Analysis Tools
library(tidyquant) # Quantitative Analysis
library(plotly)  # Interactive Visualizations


g <- c( "ATNHPIUS38060Q", # PHX Metro 
   "USSTHPI", # United States 
   "AZSTHPI")  %>% # Arizona 
  
  ## 
  tq_get(get  = "economic.data", from = "2000-01-01") %>% 
  rename(Name = symbol, Date = date, Index = price) %>%
  group_by(Name) %>%
  mutate(
    PercentChange =((Index/lag(Index,4)-1)*100) %>% round(1),
    Name = case_when(
        Name == "ATNHPIUS38060Q" ~ "Phx Metro",
        Name == "USSTHPI" ~ "United Sates",
        Name == "AZSTHPI" ~ "Arizona"),
    Name = as_factor(Name)) %>%
  na.omit %>% ungroup(Name) %>% 
  
  
  ## Data Visualization
  ggplot(aes(x=Date, y=PercentChange, color=Name)) +
  geom_line() +
  
  # Formatting
    labs(
        title = "All-Transactions House Price Indices",
        x = "Date",
        y = "YoY Percentage Change",
        caption = "Freddie Mac, retrieved from FRED:\nFederal Reserve Bank of St. Louis\nhttps://fred.stlouisfed.org") +
    theme_tq() +
    theme(
        legend.position = "right",
        axis.title.x = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(face = "italic"),
        axis.text.x = element_text(angle=30, hjust=.5),
        plot.margin = margin(1,1,1.5,1.2, "cm")) + 
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") #+ 
 # scale_y_continuous(breaks = seq(0,8,.5))

## plot 
plotly::ggplotly(g, tooltip = c("Date", "PercentChange")) %>%  
  layout(annotations = 
 list(x = 1, y = -0.1, 
      text = str_glue("Index, Not Seasonally Adjusted, Source: U.S. Federal Housing Finance Agency, retreived from fred.stlouisfed.org"), 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='bottom', yanchor='bottom', xshift=0, yshift=-40,
      font=list(size=8, color="black")) 
 )
```

Data Source:

 - [All-Transactions House Price Index for Phoenix-Mesa-Chandler, AZ](https://fred.stlouisfed.org/series/ATNHPIUS38060Q)
 - [All-Transactions House Price Index for Arizona](https://fred.stlouisfed.org/series/AZSTHPI)
 - [All-Transactions House Price Index for the United States](https://fred.stlouisfed.org/series/USSTHPI)




<br/>



```{r Avg List Prices, out.width='100%', echo=FALSE}


library(tidyverse) #Core Data Analysis Tools
library(tidyquant) # Quantitative Analysis
library(plotly)  # Interactive Visualizations


g <- c( "AVELISPRIMM38060", # PHX Metro 
   "AVELISPRIMMAZ", # Arizona
   "AVELISPRIMMUS")  %>% # US 
  
  ## 
  tq_get(get  = "economic.data", from = "2020-01-01") %>% 
  rename(Name = symbol, Date = date, Percent = price) %>%
  group_by(Name) %>%
  mutate(
    Name = case_when(
        Name == "AVELISPRIMM38060" ~ "Phx Metro",
        Name == "AVELISPRIMMAZ" ~ "Arizona",
        Name == "AVELISPRIMMUS" ~ "United States"),
    Name = as_factor(Name)) %>%
  na.omit %>% ungroup(Name) %>% 
  
  
  ## Data Visualization
  ggplot(aes(x=Date, y=Percent, color=Name)) +
  geom_line() +
  
  # Formatting
    labs(
        title = "Housing Inventory: Average Listing Price",
        x = "Date",
        y = "Month-Over-Month Percentage Change",
        caption = "Realtor.com, retrieved from FRED:\nFederal Reserve Bank of St. Louis\nhttps://fred.stlouisfed.org") +
    theme_tq() +
    theme(
        legend.position = "right",
        axis.title.x = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(face = "italic"),
        axis.text.x = element_text(angle=30, hjust=.5),
        plot.margin = margin(1,1,1.5,1.2, "cm")) + 
  scale_x_date(date_breaks = "3 month", date_labels = "%m-%y") #+ 
 # scale_y_continuous(breaks = seq(0,8,.5))

## plot 
plotly::ggplotly(g, tooltip = c("Date", "Percent")) %>%  
  layout(annotations = 
 list(x = 1, y = -0.1, 
      text = str_glue("Percent, Not Seasonally Adjusted, Source: Realtor.com, retreived from fred.stlouisfed.org"), 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='bottom', yanchor='bottom', xshift=0, yshift=-35,
      font=list(size=8, color="black")) 
 )
```


 - [Housing Inventory: Average Listing Price Month-Over-Month in Phoenix-Mesa-Scottsdale, AZ](https://fred.stlouisfed.org/series/AVELISPRIMM38060) 
 - [Housing Inventory: Average Listing Price Month-Over-Month in Arizona](https://fred.stlouisfed.org/series/AVELISPRIMMAZ)
 - [Housing Inventory: Average Listing Price Month-Over-Month in the United States]()

<br/>


```{r Day on Market, out.width='100%', echo=FALSE}

library(tidyverse) #Core Data Analysis Tools
library(tidyquant) # Quantitative Analysis
library(plotly)  # Interactive Visualizations


g <- c( "MEDDAYONMARMM38060", # PHX Metro 
   "MEDDAYONMARMMAZ", # Arizona
   "MEDDAYONMARMMUS")  %>% # US 
  
  ## 
  tq_get(get  = "economic.data", from = "2020-01-01") %>% 
  rename(Name = symbol, Date = date, Percent = price) %>%
  group_by(Name) %>%
  mutate(
    Name = case_when(
        Name == "MEDDAYONMARMM38060" ~ "Phx Metro",
        Name == "MEDDAYONMARMMAZ" ~ "Arizona",
        Name == "MEDDAYONMARMMUS" ~ "United States"),
    Name = as_factor(Name)) %>%
  na.omit %>% ungroup(Name) %>% 
  
  
  ## Data Visualization
  ggplot(aes(x=Date, y=Percent, color=Name)) +
  geom_line() +
  
  # Formatting
    labs(
        title = "Housing Inventory: Median Days on Market",
        x = "Date",
        y = "Month-Over-Month Percentage Change",
        caption = "Realtor.com, retrieved from FRED:\nFederal Reserve Bank of St. Louis\nhttps://fred.stlouisfed.org") +
    theme_tq() +
    theme(
        legend.position = "right",
        axis.title.x = element_blank(),
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(face = "italic"),
        axis.text.x = element_text(angle=30, hjust=.5),
        plot.margin = margin(1,1,1.5,1.2, "cm")) + 
  scale_x_date(date_breaks = "3 month", date_labels = "%m-%y") #+ 
 # scale_y_continuous(breaks = seq(0,8,.5))

## plot 
plotly::ggplotly(g, tooltip = c("Date", "Percent")) %>%  
  layout(annotations = 
 list(x = 1, y = -0.1, 
      text = str_glue("Percent, Not Seasonally Adjusted, Source: Realtor.com, retreived from fred.stlouisfed.org"), 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='bottom', yanchor='bottom', xshift=0, yshift=-35,
      font=list(size=8, color="black")) 
 )
```


 - [Housing Inventory: Median Days on Market Month-Over-Month in Phoenix-Mesa-Scottsdale, AZ](https://fred.stlouisfed.org/series/MEDDAYONMARMM38060) 
 - [Housing Inventory: Median Days on Market Month-Over-Month in Arizona](https://fred.stlouisfed.org/series/MEDDAYONMARMMAZ)
 - [Housing Inventory: Median Days on Market Month-Over-Month in the United States](https://fred.stlouisfed.org/series/MEDDAYONMARMMUS)
 
 

<br/>


```{r PriceReducedCount, out.width='100%', echo=FALSE}

library(tidyverse) #Core Data Analysis Tools
library(tidyquant) # Quantitative Analysis
library(plotly)  # Interactive Visualizations
library(timetk)


g <- c( "PRIREDCOU38060", # Phoenix_Metro
   "PRIREDCOU4013", # Maricopa_Co
   "PRIREDCOUAZ")  %>% #  # Arizona
  
  tq_get(get  = "economic.data", from = "2018-01-01") %>% 
  rename(Name = symbol, Date = date, Level = price) %>% 
  mutate(
    Name = case_when(
        Name == "PRIREDCOU38060" ~ "Phx_Metro",
        Name == "PRIREDCOU4013" ~ "Maricopa_Co",
        Name == "PRIREDCOUAZ" ~ "Arizona"),
    Name = as_factor(Name)) %>%
  
  ## Data Visualization
  ggplot(aes(x=Date, y=Level, color=Name)) +
  geom_line() +
  # Formatting
    labs(
        title = "Housing Inventory:Price Reduced Count",
        x = "",
        y = "Count",
        caption = "Realtor.com, retrieved from FRED:\nFederal Reserve Bank of St. Louis\nhttps://fred.stlouisfed.org") +
    
    theme_tq() +
    theme(
        legend.position = "right",
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(face = "italic"),
        axis.text.x = element_text(angle=30, hjust=.5),
        plot.margin = margin(1,1,1.5,1.2, "cm")) + 
  scale_x_date(date_breaks = "6 month", date_labels = "%m-%y") +
  scale_y_continuous(labels = scales::comma)

## plot 
plotly::ggplotly(g, tooltip = c("Date", "Level")) %>%  
  layout(annotations = 
 list(x = 1, y = -0.1, 
      text = str_glue("Level, Not Seasonally Adjusted, Source: Realtor.com, retreived from fred.stlouisfed.org"), 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='bottom', yanchor='bottom', xshift=0, yshift=-35,
      font=list(size=9, color="black"))
  )
```

Data Source:


 - [Housing Inventory: Price Reduced Count in Phoenix-Mesa-Scottsdale, AZ (CBSA)](https://fred.stlouisfed.org/series/PRIREDCOU38060)
 - [Housing Inventory: Price Reduced Count in Maricopa County, AZ](https://fred.stlouisfed.org/series/PRIREDCOU4013)
 - [Housing Inventory: Price Reduced Count in Arizona](https://fred.stlouisfed.org/series/PRIREDCOUAZ)
 


<br/>



```{r InventoryStatus, out.width='100%', echo=FALSE}

library(tidyverse) #Core Data Analysis Tools
library(tidyquant) # Quantitative Analysis
library(plotly)  # Interactive Visualizations



g <- c( "ACTLISCOU38060", # Active Listing Count PHX
   "NEWLISCOU38060", # New Listing Count PHX
   "PENLISCOU38060")  %>% #  Pending Listing Count PHX
  
  tq_get(get  = "economic.data", from = "2016-01-01") %>% 
  rename(Name = symbol, Date = date, Level = price) %>% 
  mutate(
    Name = case_when(
        Name == "ACTLISCOU38060" ~ "Active",
        Name == "NEWLISCOU38060" ~ "New",
        Name == "PENLISCOU38060" ~ "Pending"),
    Name = as_factor(Name)) %>%
  
  ## Data Visualization
  ggplot(aes(x=Date, y=Level, color=Name)) +
  geom_line() +
  
  # Formatting
    labs(
        title = "Housing Inventory: Listing Count by Status in Phoenix Metro Area",
        x = "",
        y = "Count",
        caption = "Realtor.com, retrieved from FRED:\nFederal Reserve Bank of St. Louis\nhttps://fred.stlouisfed.org") +
    
    theme_tq() +
    theme(
        legend.position = "right",
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(face = "italic"),
        axis.text.x = element_text(angle=30, hjust=.5),
        plot.margin = margin(1,1,1.5,1.2, "cm")) + 
  scale_x_date(date_breaks = "6 month", date_labels = "%m-%y") +
  scale_y_continuous(labels = scales::comma)

## plot 
plotly::ggplotly(g, tooltip = c("Date", "Level")) %>%  
  layout(annotations = 
 list(x = 1, y = -0.1, 
      text = str_glue("Level, Not Seasonally Adjusted, Source: Realtor.com, retreived from fred.stlouisfed.org"), 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='bottom', yanchor='bottom', xshift=0, yshift=-35,
      font=list(size=9, color="black"))
  )
```

Data Source: 

 - [Housing Inventory: Active Listing Count  in Phoenix-Mesa-Scottsdale](https://fred.stlouisfed.org/series/ACTLISCOU38060)  
 - [Housing Inventory: New Listing Count in Phoenix-Mesa-Scottsdale, AZ](https://fred.stlouisfed.org/series/NEWLISCOU38060)  
 - [Housing Inventory: Pending Listing Count in Phoenix-Mesa-Scottsdale, AZ](https://fred.stlouisfed.org/series/PENLISCOU38060)
 

<br/>



*Data last refreshed on `r Sys.Date()`.*

*Document Built with R Version: `r getRversion()`*
