---
title: "updateR"
author: "Matthew Dettman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Builds Website 

```{r}
library(rmarkdown)
rmarkdown::render_site(encoding = 'UTF-8')
```

# git changes

```{bash, eval=FALSE}
git add .
git commit -m "some changes"
git push --all

# paste in terminal
```

`sessionInfo()`
`code_folding: hide`


```{r, include=FALSE}

# SCRAPS
# sector_prices <- c( 
# 
# "^GSPC",     #  S&P 500 Index
# "^GSPE",     #  S&P 500 Energy 	
# "^SP500-40", #	S&P 500 Financials 	
# "^SP500-35", #  S&P 500 Health Care	
# "^SP500-60", #  S&P Real Estate
# "^SP500-15", #	S&P 500 Materials	
# "^SP500-20", #	S&P 500 Industrials
# "^SP500-25", #	S&P 500 Consumer Discretionary
# "^SP500-30", #  S&P 500 Consumer Staples
# "^SP500-45", #	S&P 500 Information Technology
# "^SP500-50", #	S&P 500 Telecommunication Services
# "^SP500-55"  #  S&P 500 Utilities
#   )  %>%   
#   tq_get(get = "stock.prices", from = (today()-365))
# 
# sector_list <- tribble(
#   
#   ~ symbol,  ~ IndexName,
#   "^GSPC",     "SP500",                   # S&P 500 Index
#   "^GSPE",     "Energy",                  # S&P 500 Energy 	  
#   "^SP500-40", "Financials",	            # S&P 500 Real Estate	
#   "^SP500-35", "HealthCare",              # S&P 500 Materials	
#   "^SP500-60", "RealEstate",	            # S&P Real Estate
#   "^SP500-15", "Materials",	              # S&P Materials
#   "^SP500-20", "Industrials",             # S&P Industrials
#   "^SP500-25", "ConsumerDiscretionary",   # S&P Consumer Discretionary
#   "^SP500-30", "ConsumerStaples",         # S&P Consumer Staples
#   "^SP500-45", "InformationTechnology",   # S&P Information Technology
#   "^SP500-50", "CommunicationServices",   # S&P Communication Services
#   "^SP500-55", "Utilities")               # S&P Utilities
# 
# SECTORS <- sector_prices %>% left_join(sector_list,by="symbol")


# 
#   
#   <!-- ## First we will create the daily returns.   -->
#   <!-- DailyReturns <- SECTORS %>% -->
#     <!--     group_by(IndexName) %>% -->
#     <!--     tq_transmute(select     = close,  -->
#                             <!--                  mutate_fun = periodReturn,  -->
#                             <!--                  period     = "daily",  -->
#                             <!--                  col_rename = "DailyReturn") %>%  -->
#     <!--   ungroup(IndexName) %>%  -->
#     <!--   mutate( -->
#                      <!--     DailyReturn = DailyReturn %>% round(2) -->
#                      <!--   ) -->
#     
#     <!-- ## Now we will create the cumulative returns.   -->
#     <!-- DailyReturnsCumulative <- DailyReturns %>% -->
#       <!--   group_by(IndexName) %>%  -->
#       <!--   mutate( -->
#                        <!--     ReturnCumulative = (cumprod(1 + DailyReturn))-1  %>% round(2) -->
#                        <!--     ) %>%  -->
#       <!--   ungroup(IndexName) -->
#       
#       <!-- Sector365plot <- ggplot(data = DailyReturnsCumulative, aes(x = date, y = ReturnCumulative, color = IndexName)) +  -->
#         <!--   geom_line() +  -->
#         <!--   scale_y_continuous(labels = scales::percent) + -->
#         <!--   ylab("Daily Return (Closing Prices)") +  -->
#         <!--   ggtitle("365 Day Sector Index Cumulative Returns") -->
#         <!-- ggplotly(Sector365plot) -->
#         <!-- ``` -->
#         





# 
# 
# ## First we will create the daily returns.
# DailyReturns <- SECTORS %>%
#   group_by(IndexName) %>%
#   tq_transmute(select     = close,
#                mutate_fun = periodReturn,
#                period     = "daily",
#                col_rename = "DailyReturn") %>%
#   ungroup(IndexName) %>%
#   mutate(
#     DailyReturn = DailyReturn %>% round(2)
#   )
# 
# ## Now we will create the cumulative returns.
# DailyReturnsCumulative <- DailyReturns %>%
#   group_by(IndexName) %>%
#   mutate(
#     ReturnCumulative = (cumprod(1 + DailyReturn))-1  %>% round(2)
#   ) %>%
#   ungroup(IndexName)
# 
# Sector365plot <- ggplot(data = DailyReturnsCumulative, aes(x = date, y = ReturnCumulative, color = IndexName)) +
#   geom_line() +
#   scale_y_continuous(labels = scales::percent) +
#   ylab("Daily Return (Closing Prices)") +
#   ggtitle("365 Day Sector Index Cumulative Returns")
# ggplotly(Sector365plot)
```

